Brownian Dynein Model

### 2015-10-06 latex/derivation.tex
Add little more to d4erivation.

@@

\begin{align}
  \Theta_{1} &= \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n}) \\
  Y_{t} &= L_n\sin(\Theta_{1}) \\
       &= L_n\sin(\cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n})) \\
       &= L_n\sqrt{1 - (\frac{L^2+L_n^2-L_f^2}{2LL_n})^2} \\
\end{align}

>>>>

We then combine terms and make the equations messier (TODO: Finish this part):

\begin{multline}
  X_{nm} = \frac{L_{s}}{L_{n}}\Bigg( \Big(\frac{2L^2L_s - L^2L_t\cos(\Theta_{nm}) + 4L_{t}L_{s}^2(\cos(\Theta_{fm})-\cos(\Theta_{nm})) - 2L_{t}^2L_{s}(\cos(\Theta_{fm})\cos(\Theta_{nm}) - \cos^2(\Theta_{nm}))}{2L}\Big) \mp \\
\hspace*{-2 cm}  L_{t}\sin(\Theta_{nm})\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s} \cos(\Theta_{nm})-\bigg(
    \frac{L^2+4L_{t}^2L_{s}^2\cos^2(\Theta_{fm})+ 4L_{t}^2L_{s}^2\cos^2(\Theta_{nm}) - 8L_{t}^2L_{s}^2\cos(\Theta_{fm})\cos(\Theta_{nm}) + 4L^2L_{t}L_{s}\cos(\Theta_{fm}) - 4L^2L_{t}L_{s}\cos(\Theta_{nm})}{2L}\bigg)} \Bigg) \\
  Y_{nm} = \frac{L_{s}}{L_{n}}\Bigg((L_{s}-L_{t}\cos(\Theta_{nm}))\sqrt{L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm})-\bigg(\frac{L^2+2L_{t}L_{s}(\cos(\Theta_{fm})-\cos(\Theta_{nm}))}{2L}\bigg)^2} \pm \\
   \frac{L^2+2L_{t}L_{s}(\cos(\Theta_{fm})-\cos(\Theta_{nm}))}{2L}L_{t}\sin(\Theta_{nm}) \Bigg) \\
\end{multline}

@@

\begin{align}
  \Theta_{1} &= \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n}) \\
  Y_{t} &= L_n\sin(\Theta_{1}) \\
  &= L_n\sin(\cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n})) \\
  &= L_n\sqrt{1 - \big(\frac{(L^2+L_n^2-L_f^2}{2LL_n}\big)^2} \\
  &= L_n\sqrt{1 - (\frac{(L^2 + L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm}) - (L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{fm})))^2}{4L^2L_n^2})} \\
  &= L_n\sqrt{1 - (\frac{(L^2 - 2L_{t}L_{s}(\cos(\Theta_{fm}) - \cos(\Theta_{nm})))^2}{4L^2L_n^2})} \\
  &= L_n\sqrt{1 - (\frac{(L^4 + 4L_{t}^2L_{s}^2(\cos^2(\Theta_{fm}) + \cos^2(\Theta_{nm}) - 2\cos(\Theta_{fm})\cos(\Theta_{nm})) - 4L^2L_{t}L_{s}(\cos(\Theta_{fm}) - \cos(\Theta_{nm})))}{4L^2(L_{s}^2+L_{t}^2-2L_{t}L_{s}\cos(\Theta_{nm}))})} \\
\end{align}
